Open science and the future university researcher\thanks{This work is licensed under a \href{https://creativecommons.org/licenses/by/4.0/}{Creative Commons Attribution 4.0 International License} \ccby}

### 2017-02-07 paper-imagine-new-university.tex
finished draft

\author[Kyle E.~Niemeyer]{Kyle E.~Niemeyer\thanks{
School of Mechanical, Industrial, \& Manufacturing Engineering,\\
\noindent Oregon State University\\
\noindent \faEnvelopeO~\href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}\\
\noindent \inlinegraphics{orcid_128x128.png}~{\scriptsize\href{https://orcid.org/0000-0003-4425-7097}{https://orcid.org/0000-0003-4425-7097}}
}}

@@

\section{Introduction to and importance of open science}
\label{sec:intro}

To me, working openly should be the default mode of science---after all, how can
we advance knowledge ``by standing on the shoulders of giants''\footnote{``If I
have seen further, it is by standing on the shoulders of giants.'' Isaac
Newton (1676), although similar statements can be found as far back as the 12th
century.} if we cannot access or see those shoulders?

This document operates on the following definition of open science:
\begin{quote}
Open science, or more broadly open research, describes the activity of performing
scientific research in a manner that makes products and findings accessible to
anyone. This includes sharing data openly (open data), publicly releasing the
source code for research software (open-source software), and making the written
products of research openly accessible (open access).
\end{quote}

@@

Since then, I have adopted the following policy for my group's research:
\begin{itemize}
    \item All written research products are made openly accessible, either through
    green or gold open-access avenues. Since my field generally lacks recognized,
    fully open-access journals, this objective is typically met by submitting
    preprints to services such as arXiv, engrXiv, or PeerJ Preprints, depending
    on the paper's topic. Conference papers, when not submitted to an open venue,
    are also made openly available through, e.g., Figshare. Where possible, all
    preprints will be released under the Creative Commons Attribution (CC-BY)
    license.\footnote{\url{https://creativecommons.org/licenses/by/4.0/legalcode}}
    (I choose, in general, to not follow the hybrid gold open-access model by
    paying a non-fully open journal.)

@@

    \item All data generated through research, when serving as the basis for
    a publication, will be archived publicly and cited appropriately in our
    work. Figures and plotting scripts will be shared via the CC-BY license
    and cited in our papers.
\end{itemize}
This policy will be implemented in part by incorporating its content into
funding proposals, for example in Data Management Plans.

@@

Instead, cultural inertia and lack of institutional recognition\slash rewards pose
the most significant challenges to increased openness in science. In my opinion,
the biggest barrier is that most researchers either disagree on or are unaware of
the importance (and benefits) of working openly. Since they were not trained in
doing this, e.g., during graduate school or during postdoctoral training, they
also may simply be unaware of how to research openly, or the resources that are
available to do so. Furthermore, since most of their colleagues, collaborators,
and competitors do not practice open science, no pressure comes from the
research community to change. In addition, some communities do not support or
actively oppose activities such as submitting preprints.

This lack of pressure is related to the other major issue: lack of institutional
recognition and reward for open practices. In general, academic researchers will
do what gets them credit for promotion and tenure---anything beyond that requires
strong intrinsic motivation.

>>>>

\author[Kyle E.~Niemeyer]{Kyle E.~Niemeyer\thanks{
School of Mechanical, Industrial, \& Manufacturing Engineering,\\
\noindent Oregon State University\\
\noindent \href{mailto:kyle.niemeyer@oregonstate.edu}{\faEnvelopeO{}~kyle.niemeyer@oregonstate.edu}\\
\noindent \href{https://orcid.org/}{\inlinegraphics{orcid_128x128.png}}~{\scriptsize\href{https://orcid.org/0000-0003-4425-7097}{https://orcid.org/0000-0003-4425-7097}}
}}

@@

\section{Introduction}
\label{sec:intro}

Working openly should be the default mode of science---after all, how can
we advance knowledge ``by standing on the shoulders of giants''\footnote{``If I
have seen further, it is by standing on the shoulders of giants.'' Isaac
Newton (1676), although similar statements can be found as far back as the 12th
century.} if we cannot access or see those shoulders? This paper operates
on the following definition of open science:
\begin{quote}
Open science, or more broadly open research, describes the activity of performing
scientific research in a manner that makes products and findings accessible to
anyone. This includes sharing data openly (open data), publicly releasing the
source code for research software (open-source software), and making the written
products of research openly accessible (open access).
\end{quote}
In this paper, I describe my views on why open science practices are important
(supported by relevant studies), and discuss the potential societal impact of
increased openness. I also summarize my policy towards open science in my
research agenda. Finally, I call out pressing challenges to increased openness
in research, and lay out four recommended changes for university leaders that
could help encourage faculty to adopt better open practices in their research.

\section{Importance of open science}
\label{sec:importance}

@@

Since then, I have adopted the following policy for my group's research:
\begin{itemize}
    \item All written research products are made openly accessible, either through
    green or gold open-access avenues. Since my field generally lacks recognized,
    fully open-access journals, this objective is typically met by submitting
    preprints to services such as arXiv, engrXiv, or PeerJ Preprints, depending
    on the paper's topic. Conference papers, when not submitted to an open venue,
    are also made openly available through, e.g., Figshare. Where possible, all
    preprints will be released under the Creative Commons Attribution (CC BY)
    license.\footnote{\url{https://creativecommons.org/licenses/by/4.0/legalcode}}
    (I choose, in general, to not follow the hybrid gold open-access model by
    paying a non-fully open journal.)

@@

    \item All data generated through research, when serving as the basis for
    a publication, will be archived publicly and cited appropriately in our
    work. Figures and plotting scripts will be shared via the CC BY license
    and cited in our papers.
\end{itemize}
This policy will be implemented in part by incorporating its content into
funding proposals, for example in Data Management Plans.

@@

Instead, cultural inertia and lack of institutional recognition\slash rewards pose
the most significant challenges to increased openness in science.

In my opinion, the biggest barrier to greater openness in research is ambivalence
or outright hostility in many research communities. Many academic researchers
either disagree on or are unaware of the importance (and benefits) of working
openly. Since they were not trained in doing this, e.g., during graduate school
or during postdoctoral training, they also may simply be unaware of how to
research openly, or the resources that are available to do so.
Furthermore, since most of their colleagues, collaborators,
and competitors do not practice open science, no pressure comes from the
research community to change. In addition, some communities do not support or
actively oppose activities such as submitting preprints.

This lack of pressure is related to the other major issue: lack of institutional
recognition and reward for open practices. In general, academic researchers will
work on what gets them credit for promotion and tenure---anything beyond that
requires strong intrinsic motivation, or external motivators from the research
community. At most institutions, promotion and tenure review includes some
judgement (whether explicit or implicit) of where faculty publish their work,
but many, ``high-impact''' traditional publication venues---particularly domain
journals---may not support, e.g., the posting of preprints.

\section{Recommendations for university leaders}
\label{sec:recommendations}

%Some funding agencies have begun to mandate that the researchers they fund share
%the products of their work openly.

The following list of recommendations are mostly targeted at changing criteria
for promotion and tenure, and performance reviews, to encourage faculty to
practice more open science:
\begin{itemize}
    \item Consider accessibility\slash openness of research products along
    with quantity and ``quality'' in promotion and tenure review.

    \item Recognize research products such as software and data, and their
    associated impacts (e.g., citations), as equal to traditional
    publications in scholarly impact.

    \item Reduce the importance of publishing in traditional venues for promotion
    and tenure, recognizing these may be barriers to openness.

    \item Support efforts to teach undergraduate and graduate students about
    open science skills, and those necessary to work with software and data, with
    the same enthusiasm that traditional lab courses receive.
\end{itemize}
Research communities that impede openness cannot be forced to change from the
outside. Instead, by making changes to institutional award systems, researchers
will be encouraged to improve their open practices, and thus evolve communities
from the inside.
